\begin{acknowledgements}

The work performed for this dissertation was only possible 
with the help and guidance of many mentors, colleagues, and friends,
to whom I would like to express my gratitude.
%
First, I would like to thank my advisor, Claudio Campagnari, for
supporting me since my arrival five years ago and for teaching
me much of what I know about experimental particle physics.
I could not have asked for a better mentor.

Frank Golf and Indara Suarez provided much-needed guidance and direction
during the early years of my graduate research. 
It was a joy working with them and everyone else in Claudio's
group, including Nick Amin, Sicheng Wang, Franny Setti,
Ulascan Sarica, Hualin Mei, Jonathan Guiang, Jerry Ling, and Japnidh Thakral.
I would especially like to thank Nick and Sicheng for being great
co-workers and friends from my first day at UCSB
(and much of the work done here would have been significantly
harder without Nick's various secret projects.
Thank you for DIS and Metis.)

My work would not have been possible without the knowledge
and technical support provided by the many professors, post-docs, and
graduate students comprising the Surf-n-Turf collaboration.
In particular, Dominick Olivito and Giovanni Zevi Della Porta showed me the ropes of the \mttwo analysis,
and Dylan Gilbert, Mario Masciovecchio, Slava Krutelyov, and Avi Yagil
were invaluable partners and mentors in the push to complete its latest iteration.

I started work with the milliQan experiment in my first month as a graduate student, and finished with
its first public result in my final week. I have greatly enjoyed working on this unique
project throughout my time here with everyone involved at UCSB and elsewhere. In addition
to those already mentioned above, I learned a tremendous amount from
David Stuart, who has acted many times as almost a second advisor for this and other projects.
Matthew Citron provided much guidance in our efforts to extract
useful physics from the prototype detector.

Finally, I must thank my family for everything they have provided me. My parents Jim and Janice Marsh
have unconditionally supported me always, and encouraged my passion for science from an early age.
I would not have had the opportunities I have had without them.
And to my lovely wife, Amber, who moved to California and put up with the grad school life for five years
as I pursued my goals. I would not have been able to do this without your support, and I am so excited
to start the next chapter of our lives together.


\end{acknowledgements} 
