\begin{vitae}
\addcontentsline{toc}{chapter}{Curriculum Vitae}

\begin{vitaesection}{Education}
\vspace{-0.1cm}
\item [2020] Ph.D. in Physics, University of California, Santa Barbara.
\item [2018] M.A. in Physics, University of California, Santa Barbara.
\item [2015] B.S. in Physics and Mathematics, Purdue University, West Lafayette, IN.
\end{vitaesection}

\vspace{0.5cm}
\textbf{Publications}

%% \nobibliography*
%% \begin{itemize}
    %% \item \bibentry{GAN:LHC2019} % http://inspirehep.net/record/1714018
    %% \item \bibentry{CMS:myTOPRun2PAS} % http://inspirehep.net/record/1726177
    %% \item \bibentry{CMS:mySUSRun2PAS} % http://inspirehep.net/record/1726691
    %% \item \bibentry{CMS:myTOP2016} % http://inspirehep.net/record/1633423
    %% \item \bibentry{CMS:mySUS2016} % http://inspirehep.net/record/1594731
%% \end{itemize}

\begin{itemize}

\item CMS Collaboration, ``Searches for physics beyond the standard model with the $M_\mathrm{T2}$ variable in hadronic
  final states with and without disappearing tracks in proton-proton collisions at $\sqrt{s}=13~\mathrm{TeV}$.''
  \textit{Eur. Phys. J. C} \textbf{80} (2020), 3.
  [\href{https://arxiv.org/abs/1909.03460}{arXiv:1909.03460}].

\item CMS Collaboration, ``Constraints on models of scalar and vector leptoquarks decaying to a quark
  and a neutrino at $\sqrt{s}=13~\mathrm{TeV}$.'' \textit{Phys. Rev. D}
  \textbf{98} (2018), 032005. 
  [\href{https://arxiv.org/abs/1805.10228}{arXiv:1805.10228}].

\item CMS Collaboration, ``Search for new phenomena with the $M_\mathrm{T2}$ variable in the all-hadronic
  final state produced in proton-proton collisions at $\sqrt{s}=13~\mathrm{TeV}$.'' \textit{Eur. Phys J. C}
  \textbf{77} (2017), 710.
  [\href{https://arxiv.org/abs/1705.04650}{arXiv:1705.04650}].

\item Ball, A. et al. ``A Letter of Intent to Install a Milli-charged Particle Detector at LHC P5''. July 2016.
  [\href{https://arxiv.org/abs/1607.04669}{arXiv:1607.04669}].

\end{itemize}


\vspace{0.2cm}
\textbf{Public Talks}

\begin{itemize}

\item ``The milliQan experiment: a search for milli-charged particles at the LHC''.
Light Dark Matter @ Accelerators Workshop, Nov. 20--22, 2019. Venice, Italy.

\item ``Monitoring tools for the muon system in the Compact Muon Solenoid (CMS) detector''.
Machine Learning in Science and Engineering Conference, June 6--8, 2018. Carnegie Mellon
University, Pittsburgh, PA.

\end{itemize}

\end{vitae}
